iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-29 manuscript/main.tex
Added numbers to all use cases.

\subsection*{Plate-based single-cell RNA sequencing}
To demonstrate iSEE's functionality, we used it to explore a plate-based single-cell RNA sequencing (scRNA-seq) data set.
We used a subset of data from a study involving cells from the mouse visual cortex \citep{tasic2016allen}.
This demonstration guides the user through the main features of the iSEE interface, including the multi-panel layout, colouring options and dynamic linking.\\

@@

\subsection*{Mass cytometry}
Finally, we explored a mass cytometry study involving PBMCs from multiple donors before and after stimulation with BCR/FcR-XL \citep{bodenmiller2012cytof}.
We used iSEE to vizualise and refine a gating analysis to obtain B cells, and to investigate differences in expression of the functional marker pS6 after stimulation.\\

>>>>

\subsection*{Plate-based single-cell RNA sequencing}
To demonstrate iSEE's functionality, we used it to explore a plate-based single-cell RNA sequencing (scRNA-seq) data set involving 379 cells from the mouse visual cortex \citep{tasic2016allen}.
This demonstration guides the user through the main features of the iSEE interface including the multi-panel layout, colouring and dynamic linking.\\

@@

\subsection*{Mass cytometry}
Finally, we explored a mass cytometry study involving 150,000 PBMCs from multiple donors before and after stimulation with BCR/FcR-XL \citep{bodenmiller2012cytof}.
We used iSEE to vizualise and refine a gating analysis to obtain B cells, and to investigate differences in expression of the functional marker pS6 after stimulation.\\
